---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = F
)
```

# Hvsp

<!-- badges: start -->
<!-- badges: end -->

This package implements the Hierarchical Vintage Sparse PCA (`Hvsp`) methodology
and is built upon the [`HCD` package](https://cran.r-project.org/web/packages/HCD/index.html).

* `Hvsp()` produces the centrality estimation and regression coefficient estimation of the commonly used two-stage procedure.

It also includes functions in the `HCD` package:

* `HCD()` applies the hierarchical community detection (HCD) by Li et al. (2020).
* `BTSBM()` generates network from the binary tree stochastic block model by Li et al. (2020).

## Installation

You can install the development version of `Hvsp` from [GitHub](https://github.com/Hvsp) with:

```{r}
if (!require("devtools")){
    install.packages("devtools")
}
devtools::install_github("cccfran/Hvsp")
```

## Example

This is a basic example which shows you how to use `Hvsp` on a network:

```{r}
library(Hvsp)

# load a citation network
data(citation)

# apply citation network
Hvsp(citation)
```
